### 2023-03-29 response-to-audit-report.md

-      ("Escrow"          , Escrow.escrow (v 900_000_000) alice bob charlie 100 200 300 400)
-    , ("Forward"         , Forward.forward alice a (v 10) 100 bob b (v 20) 200 300)
-    , ("Future"          , Futures.future alice bob (v 100) (v 200) 100 [200] 500)
-    , ("Swap"            , Swap.swap alice a (v 100) 100 bob b (v 200) 200 E.Close)
-    , ("Trivial"         , Trivial.trivial alice 100_000_000 70_000_000 0)
-    , ("Zero-Coupon Bond", ZeroCouponBond.zeroCouponBond alice bob 100 200 (v 100_000_000) (v 200_000_000) c E.Close)
-    ]
-
-
--- | A request to the semantics oracle.
-data OracleRequest =
-  OracleRequest
-  {
-    request          :: String
-  , state            :: State
-  , transactionInput :: TransactionInput
-  , coreContract     :: Contract
-  }
-  deriving (Generic, Show)
-
-instance FromJSON OracleRequest
-
-instance ToJSON OracleRequest
-
-
--- | A response from the semantics oracle.
-data OracleResponse =
-    TransactionSuccess TransactionOutput
-  | TransactionError
-  deriving (Generic, Show)
-
-instance FromJSON OracleResponse where
-  parseJSON =
-    withObject "OracleResponse"
-      $ \o ->
-        do
-          success <- o .: "transaction_success"
-          txOutWarnings <- success .: "txOutWarnings"
-          payments      <- success .: "txOutPayments"
-          txOutState    <- success .: "txOutState"
-          txOutContract <- success .: "txOutContract"
-          txOutPayments <- mapM paymentFromJSON payments
-          pure . TransactionSuccess $ TransactionOutput{..}
-
-
-instance ToJSON OracleResponse where
-  toJSON (TransactionSuccess TransactionOutput{..}) =
-    object
-      [
-        "transaction_success" .= object
-                                   [
-                                     "txOutWarnings" .= toJSON txOutWarnings
-                                   , "txOutPayments" .= fmap paymentToJSON txOutPayments
-                                   , "txOutState"    .= toJSON txOutState
-                                   , "txOutContract" .= toJSON txOutContract
-                                   ]
-      ]
-  toJSON _ = "transaction_error"
-
-
--- | Deserialize a payment from JSON.
-paymentFromJSON :: Value -> Parser Payment
-paymentFromJSON =
-  withArray "Payment"
-    $ \v ->
-      do
-        a <- parseJSON $ v ! 0
-        p <- parseJSON $ v ! 1
-        [(c, [(n, i)])] <- parseJSON (v ! 2)
-        pure $ Payment a p (Token (fromString c) (fromString n)) i
-
-
--- | Serialize a payment to JSON.
-paymentToJSON :: Payment -> Value
-paymentToJSON (Payment a p t i) =
-  Array
-    $ V.fromList
-    [
-      toJSON a
-    , toJSON p
-    , toJSON t
-    , toJSON i
-    ]
-
-
--- | Equality test for transaction output.
-eqTransactionOutput :: TransactionOutput -> TransactionOutput -> Bool
-eqTransactionOutput x@TransactionOutput{} y@TransactionOutput{} =
-     txOutWarnings x == txOutWarnings y
-  && txOutPayments x == txOutPayments y
-  && txOutState    x ~~ txOutState    y
-  && txOutContract x == txOutContract y
-eqTransactionOutput _ _ = False
-
-
--- | Equality test for state.
-(~~) :: State -> State -> Bool
-x ~~ y =
-     accounts    x `eqAssocMap` accounts    y
-  && choices     x `eqAssocMap` choices     y
-  && boundValues x `eqAssocMap` boundValues y
-  && minTime     x ==           minTime     y
-
-
--- | Equality test for association lists.
-eqAssocMap :: Ord k => Ord v => AM.Map k v -> AM.Map k v -> Bool
-eqAssocMap = (==) `on` (sort . AM.toList)
-
-
--- | Use static analysis to generate paths through a contract, and then compare execution to the oracle.
-compareToOracle :: Handle -> Handle -> String -> E.Contract -> IO ()
-compareToOracle hToOracle hFromOracle name extended =
-  do
-    Just core <- pure $ E.toCore extended
-    Right paths <- getAllInputs core
-    let
-      accounts = AM.empty
-      choices = AM.empty
-      boundValues = AM.empty
-      request = "compute-transaction"
-    sequence_
-      [
-        let
-          go _ _ _ [] = pure ()
-          go j state coreContract (transactionInput : transactionInputs) =
-            do
-              hPutStrLn hToOracle "```"
-              hPutStrLn hToOracle $ LBS8.unpack $ encode OracleRequest{..}
-              hPutStrLn hToOracle "```"
-              result <- hGetLine hFromOracle
-              actual@TransactionOutput{..} <- pure $ computeTransaction transactionInput state coreContract
-              Right (TransactionSuccess expected) <- pure $ eitherDecode $ LBS8.pack result
-              let match = actual `eqTransactionOutput` expected
-              assertBool (name <> ", path " <> show (i :: Int) <> ", step " <> show (j :: Int)) match
-              go (j + 1) txOutState txOutContract transactionInputs
-        in
-          go 1 State{..} core inputs
-      |
-        (i, (minTime, inputs)) <- zip [1..] paths
-      ]
diff --git a/marlowe-test/src/Spec/Marlowe/Serialization/CoreJson.hs b/marlowe-test/src/Spec/Marlowe/Serialization/CoreJson.hs
index a3c456b9d..3420569d3 100644
--- a/marlowe-test/src/Spec/Marlowe/Serialization/CoreJson.hs
+++ b/marlowe-test/src/Spec/Marlowe/Serialization/CoreJson.hs
@@ -9,12 +9,16 @@
 -- | This suite tests the Json serialization of the Marlowe core module
 --
 -----------------------------------------------------------------------------
+
+
 {-# LANGUAGE OverloadedStrings #-}

+
 module Spec.Marlowe.Serialization.CoreJson
   ( tests
   ) where

+
 import Control.Arrow (Arrow((***)))
 import Data.Aeson (decode, encode)
 import Data.ByteString (ByteString)
@@ -28,6 +32,7 @@ import Test.QuickCheck.Property (forAll, forAllShrink, withMaxSuccess)
 import Test.Tasty (TestTree, testGroup)
 import Test.Tasty.QuickCheck (testProperty)

+
 tests :: TestTree
 tests = testGroup "Core Contract Serialization"
     [ testProperty "Serialise deserialise Contract loops" prop_contractJsonLoops
@@ -40,6 +45,7 @@ tests = testGroup "Core Contract Serialization"
 contractJsonLoops :: Contract -> Property
 contractJsonLoops cont = decode (encode cont) === Just cont

+
 -- | Test that JSON decoding inverts encoding for contracts.
 prop_contractJsonLoops :: Property
 prop_contractJsonLoops = withMaxSuccess 1000 $ forAllShrink contractGen shrinkContract contractJsonLoops
@@ -50,6 +56,7 @@ prop_contractJsonLoops = withMaxSuccess 1000 $ forAllShrink contractGen shrinkCo
 marloweParamsJsonLoops :: MarloweParams -> Property
 marloweParamsJsonLoops mp = decode (encode mp) === Just mp

+
 -- | Test that JSON decoding inverts encoding for Marlowe parameters.
 prop_marloweParamsJsonLoops :: Property
 prop_marloweParamsJsonLoops = withMaxSuccess 1000 $ forAll gen marloweParamsJsonLoops
@@ -58,6 +65,7 @@ prop_marloweParamsJsonLoops = withMaxSuccess 1000 $ forAll gen marloweParamsJson
       c <- toBuiltin <$> (arbitrary :: Gen ByteString)
       return $ MarloweParams (CurrencySymbol c)

+
 -- | Test that JSON decoding inverts encoding for an interval error.
 intervalErrorJsonLoops :: IntervalError -> Property
 intervalErrorJsonLoops ie = decode (encode ie) === Just ie
diff --git a/marlowe-test/src/Spec/Marlowe/Serialization/ExtendedJson.hs b/marlowe-test/src/Spec/Marlowe/Serialization/ExtendedJson.hs
index b93984ddd..0c357bbf4 100644
--- a/marlowe-test/src/Spec/Marlowe/Serialization/ExtendedJson.hs
+++ b/marlowe-test/src/Spec/Marlowe/Serialization/ExtendedJson.hs
@@ -9,18 +9,23 @@
 -- | This suite tests the Json serialization of the Marlowe extended module
 --
 -----------------------------------------------------------------------------
+
+
 {-# LANGUAGE OverloadedStrings #-}

+
 module Spec.Marlowe.Serialization.ExtendedJson
   ( tests
   ) where

+
 import Data.Aeson (eitherDecodeFileStrict)
 import Language.Marlowe.Extended.V1 (Contract, Module)
 import System.FilePath ((</>))
 import Test.Tasty (TestTree, testGroup)
 import Test.Tasty.HUnit (assertFailure, testCase)

+
 tests :: TestTree
 tests = testGroup "Extended Contract Serialization"
     [ testCase "Golden Swap contract" testGoldenSwapContract
@@ -29,9 +34,11 @@ tests = testGroup "Extended Contract Serialization"

 -- TODO: Do a small non-property round-trip with example contracts.

+
 goldenPath :: FilePath
 goldenPath = "test" </> "Spec" </> "Marlowe" </> "Serialization" </> "golden"

+
 -- | Checks that we can decode the Golden JSON Contract for Swap
 testGoldenSwapContract :: IO ()
 testGoldenSwapContract = do
@@ -40,6 +47,7 @@ testGoldenSwapContract = do
         Left err              -> assertFailure err
         Right (_ :: Contract) -> return ()

+
 -- | Checks that we can decode the Golden JSON Module for Swap
 -- | TODO: If we are more of these tests, add a helper function with a Proxy type
 testGoldenSwapModule :: IO ()
diff --git a/marlowe-test/src/Spec/Marlowe/Service.hs b/marlowe-test/src/Spec/Marlowe/Service.hs
new file mode 100644
index 000000000..e02ef56f8
--- /dev/null
+++ b/marlowe-test/src/Spec/Marlowe/Service.hs
@@ -0,0 +1,73 @@
+-----------------------------------------------------------------------------
+--
+-- Module      :  $Headers
+-- License     :  Apache 2.0
+--
+-- Stability   :  Experimental
+-- Portability :  Portable
+--
+-- | Client for Isabelle-based Marlowe testing service.
+--
+-----------------------------------------------------------------------------
+
+
+{-# LANGUAGE LambdaCase #-}
+{-# LANGUAGE OverloadedStrings #-}
+{-# LANGUAGE RecordWildCards #-}
+
+
+module Spec.Marlowe.Service
+  ( -- * Testing
+    handle
+  , handleValues
+  ) where
+
+
+import Spec.Marlowe.Service.Random (generateValue)
+import Spec.Marlowe.Service.Serialization (roundtripSerialization)
+import Spec.Marlowe.Service.Types (Request(..), Response(..))
+
+import qualified Data.Aeson as A (Result(..), Value, fromJSON, object, toJSON, (.=))
+import qualified Language.Marlowe.Core.V1.Semantics as Marlowe
+  (computeTransaction, evalObservation, evalValue, playTrace)
+
+
+-- | Respond to a request expressed as JSON.
+handleValues :: A.Value -> IO A.Value
+handleValues request =
+  case A.fromJSON request of
+    A.Success request' -> A.toJSON <$> handle request'
+    A.Error message -> error message
+
+
+-- | Respond to a request.
+handle :: Request -> IO Response
+handle TestRoundtripSerialization{..} =
+  pure
+    . RequestResponse . A.toJSON
+    $ roundtripSerialization typeSerialized valueSerialized
+handle GenerateRandomValue{..} =
+  generateValue size seed typeSerialized
+    >>= \case
+      Right value -> pure . RequestResponse . A.object . pure $ "value" A..= value
+      Left failureResponse -> pure $ ResponseFailure{..}
+handle ComputeTransaction{..} =
+  let
+    valueResponse = A.toJSON $ Marlowe.computeTransaction transactionInput state contract
+  in
+    pure RequestResponse{..}
+handle PlayTrace{..} =
+  let
+    valueResponse = A.toJSON $ Marlowe.playTrace initialTime contract transactionInputs
+  in
+    pure RequestResponse{..}
+handle EvalValue{..} =
+  let
+    valueResponse = A.toJSON $ Marlowe.evalValue environment state value
+  in
+    pure RequestResponse{..}
+handle EvalObservation{..} =
+  let
+    valueResponse = A.toJSON $ Marlowe.evalObservation environment state observation
+  in
+    pure RequestResponse{..}
diff --git a/marlowe-test/src/Spec/Marlowe/Service/Isabelle.hs b/marlowe-test/src/Spec/Marlowe/Service/Isabelle.hs
new file mode 100644
index 000000000..f4c5fcf0e
--- /dev/null
+++ b/marlowe-test/src/Spec/Marlowe/Service/Isabelle.hs
@@ -0,0 +1,39 @@
+-----------------------------------------------------------------------------
+--
+-- Module      :  $Headers
+-- License     :  Apache 2.0
+--
+-- Stability   :  Experimental
+-- Portability :  Portable
+--
+-- | Test Marlowe's Cardano implementation against the Isabelle-derived test server.
+--
+-----------------------------------------------------------------------------
+
+
+module Spec.Marlowe.Service.Isabelle
+  ( -- * Testing
+    tests
+  ) where
+
+
+import Spec.Marlowe.Service (handleValues)
+import Test.Tasty (TestTree, testGroup)
+
+import qualified Data.Aeson as A
+import qualified Marlowe.Spec.Core (tests)
+
+
+-- | Run the tests.
+tests :: TestTree
+tests =
+  testGroup "Marlowe Client"
+    [
+      Marlowe.Spec.Core.tests
+        $ \request ->
+          do
+            response <- handleValues $ A.toJSON request
+            case A.fromJSON response of
+              A.Success response' -> pure response'
+              A.Error message -> error message
+    ]
diff --git a/marlowe-test/src/Spec/Marlowe/Service/Random.hs b/marlowe-test/src/Spec/Marlowe/Service/Random.hs
new file mode 100644
index 000000000..5a312aa0f
--- /dev/null
+++ b/marlowe-test/src/Spec/Marlowe/Service/Random.hs
@@ -0,0 +1,44 @@
+-----------------------------------------------------------------------------
+--
+-- Module      :  $Headers
+-- License     :  Apache 2.0
+--
+-- Stability   :  Experimental
+-- Portability :  Portable
+--
+-- | Arbitrary instance for an existentially quantified JSON type.
+--
+-----------------------------------------------------------------------------
+
+
+module Spec.Marlowe.Service.Random
+  ( -- * Testing
+    generateValue
+  ) where
+
+
+import Data.Jsonable (generateJsonable)
+import Spec.Marlowe.Semantics.Arbitrary ()
+import Spec.Marlowe.Service.Serialization (knownJsonTypes)
+import Spec.Marlowe.Service.Types (Seed(..), Size(..))
+import Test.QuickCheck (generate)
+import Test.QuickCheck.Gen (Gen(..))
+import Test.QuickCheck.Random (mkQCGen, newQCGen)
+
+import qualified Data.Aeson as A (Value)
+
+
+-- | Generate an arbitrary value.
+generateValue
+  :: Maybe Size  -- ^ The optional size paramater.
+  -> Maybe Seed  -- ^ The optional seed for the generator.
+  -> String  -- ^ The key for the type.
+  -> IO (Either String A.Value)  -- ^ Either the value or an error message.
+generateValue size seed =
+  mapM (generate' size seed) . generateJsonable knownJsonTypes
+  where
+    generate' :: Maybe Size -> Maybe Seed -> Gen a -> IO a
+    generate' (Just (Size s)) (Just (Seed r)) (MkGen g) = return $ g (mkQCGen r) s
+    generate' Nothing (Just (Seed r)) (MkGen g) = return $ g (mkQCGen r) 30
+    generate' (Just (Size s)) Nothing (MkGen g) = newQCGen >>= \r -> return $ g r s
+    generate' _ _ g = generate g
diff --git a/marlowe-test/src/Spec/Marlowe/Service/Serialization.hs b/marlowe-test/src/Spec/Marlowe/Service/Serialization.hs
new file mode 100644
index 000000000..08a373eb9
--- /dev/null
+++ b/marlowe-test/src/Spec/Marlowe/Service/Serialization.hs
@@ -0,0 +1,106 @@
+-----------------------------------------------------------------------------
+--
+-- Module      :  $Headers
+-- License     :  Apache 2.0
+--
+-- Stability   :  Experimental
+-- Portability :  Portable
+--
+-- | Test of Marlowe's Cardano JSON implementation against the reference implementation.
+--
+-----------------------------------------------------------------------------
+
+
+{-# LANGUAGE OverloadedStrings #-}
+{-# LANGUAGE RecordWildCards #-}
+
+
+module Spec.Marlowe.Service.Serialization
+  ( -- * Types
+    SerializationResponse(..)
+  , knownJsonTypes
+    -- * Testing
+  , roundtripSerialization
+  ) where
+
+
+import Control.Applicative ((<|>))
+import Data.Aeson (FromJSON(..), ToJSON(..))
+import Data.Jsonable (JsonableType(JsonableType), KnownJsonable, isKnownJson, roundTripJsonable)
+import Data.Proxy (Proxy(..))
+import Spec.Marlowe.Semantics.Arbitrary ()
+
+import qualified Data.Aeson as A (Value, object, withObject, (.:), (.=))
+import qualified Language.Marlowe.Core.V1.Semantics as Marlowe
+import qualified Language.Marlowe.Core.V1.Semantics.Types as Marlowe
+
+
+-- | Response to a round-trip serialization request.
+data SerializationResponse =
+    -- | Success.
+    SerializationSuccess
+    {
+      valueReserialized :: A.Value  -- ^ The reserialized value.
+    }
+    -- | The type was not known.
+  | UnknownType
+    {
+      unknownType :: String  -- ^ The type.
+    }
+    -- | The deserialization or serialization failed.
+  | SerializationError
+    {
+      serializationError :: String  -- ^ The error message.
+    }
+  deriving (Eq, Ord, Read, Show)
+
+instance ToJSON SerializationResponse where
+  toJSON SerializationSuccess{..} = A.object . pure $ "serialization-success" A..= valueReserialized
+  toJSON UnknownType{..} = A.object . pure $ "unknown-type" A..= unknownType
+  toJSON SerializationError{..} = A.object . pure $ "serialization-error" A..= serializationError
+

### 2023-03-29 response-to-audit-report.md

+instance FromJSON SerializationResponse where
+  parseJSON =
+    A.withObject "SerializationResponse"
+      $ \o ->
+            (SerializationSuccess <$> o A..: "serialization-success")
+        <|> (UnknownType <$> o A..: "unknown-type")
+        <|> (SerializationError <$> o A..: "serialization-error")
+
+
+-- | Deserialize and then serialize a value.
+roundtripSerialization
+  :: String  -- ^ The key to the type.
+  -> A.Value  -- ^ The value.
+  -> SerializationResponse  -- ^ The result.
+roundtripSerialization typeSerialized valueSerialized =
+  if isKnownJson knownJsonTypes typeSerialized
+    then case roundTripJsonable knownJsonTypes typeSerialized valueSerialized of
+             Right valueReserialized -> SerializationSuccess{..}
+             Left serializationError -> SerializationError{..}
+    else UnknownType typeSerialized
+
+
+-- | List of known types that can be serialized and deserialized as JSON.
+knownJsonTypes :: KnownJsonable
+knownJsonTypes =
+  [
+    JsonableType "Core.Action" (Proxy :: Proxy Marlowe.Action)
+  , JsonableType "Core.Bound" (Proxy :: Proxy Marlowe.Bound)
+  , JsonableType "Core.Case" (Proxy :: Proxy (Marlowe.Case Marlowe.Contract))
+  , JsonableType "Core.ChoiceId" (Proxy :: Proxy Marlowe.ChoiceId)
+  , JsonableType "Core.Contract" (Proxy :: Proxy Marlowe.Contract)
+  , JsonableType "Core.Token" (Proxy :: Proxy Marlowe.Token)
+  , JsonableType "Core.Payee" (Proxy :: Proxy Marlowe.Payee)
+  , JsonableType "Core.Input" (Proxy :: Proxy Marlowe.Input)
+  , JsonableType "Core.Observation" (Proxy :: Proxy Marlowe.Observation)
+  , JsonableType "Core.Value" (Proxy :: Proxy (Marlowe.Value Marlowe.Observation))
+  , JsonableType "Core.Party" (Proxy :: Proxy Marlowe.Party)
+  , JsonableType "Core.State" (Proxy :: Proxy Marlowe.State)
+  , JsonableType "Core.Payment" (Proxy :: Proxy Marlowe.Payment)
+  , JsonableType "Core.Transaction" (Proxy :: Proxy Marlowe.TransactionInput)
+  , JsonableType "Core.TransactionOutput" (Proxy :: Proxy Marlowe.TransactionOutput)
+  , JsonableType "Core.TransactionWarning" (Proxy :: Proxy Marlowe.TransactionWarning)
+  , JsonableType "Core.TransactionError" (Proxy :: Proxy Marlowe.TransactionError)
+  , JsonableType "Core.IntervalError" (Proxy :: Proxy Marlowe.IntervalError)
+  ]
diff --git a/marlowe-test/src/Spec/Marlowe/Service/Types.hs b/marlowe-test/src/Spec/Marlowe/Service/Types.hs
new file mode 100644
index 000000000..6bcbb7579
--- /dev/null
+++ b/marlowe-test/src/Spec/Marlowe/Service/Types.hs
@@ -0,0 +1,172 @@
+-----------------------------------------------------------------------------
+--
+-- Module      :  $Headers
+-- License     :  Apache 2.0
+--
+-- Stability   :  Experimental
+-- Portability :  Portable
+--
+-- | Marlowe types for the test service client.
+--
+-----------------------------------------------------------------------------
+
+
+{-# LANGUAGE GeneralizedNewtypeDeriving #-}
+{-# LANGUAGE LambdaCase #-}
+{-# LANGUAGE OverloadedStrings #-}
+{-# LANGUAGE RecordWildCards #-}
+
+
+module Spec.Marlowe.Service.Types
+  ( -- * Types
+    Request(..)
+  , Response(..)
+  , Seed(..)
+  , Size(..)
+  ) where
+
+
+import Control.Applicative ((<|>))
+import Data.Aeson (FromJSON(..), ToJSON(..))
+import Plutus.V1.Ledger.Api (POSIXTime(..))
+
+import qualified Data.Aeson as A (Value(Object, String), object, withObject, (.:), (.:?), (.=))
+import qualified Data.Aeson.Types as A (Parser)
+import qualified Language.Marlowe.Core.V1.Semantics as Marlowe
+import qualified Language.Marlowe.Core.V1.Semantics.Types as Marlowe
+
+newtype Size = Size Int deriving (Eq, Show, ToJSON, FromJSON)
+newtype Seed = Seed Int deriving (Eq, Show, ToJSON, FromJSON)
+
+data Request =
+    TestRoundtripSerialization
+    {
+      typeSerialized :: String
+    , valueSerialized :: A.Value
+    }
+  | GenerateRandomValue
+    {
+      typeSerialized :: String
+    , size :: Maybe Size
+    , seed :: Maybe Seed
+    }
+  | ComputeTransaction
+    {
+      transactionInput :: Marlowe.TransactionInput
+    , contract :: Marlowe.Contract
+    , state :: Marlowe.State
+    }
+  | PlayTrace
+    {
+      transactionInputs :: [Marlowe.TransactionInput]
+    , contract :: Marlowe.Contract
+    , initialTime :: POSIXTime
+    }
+  | EvalValue
+    {
+      environment :: Marlowe.Environment
+    , state :: Marlowe.State
+    , value :: Marlowe.Value Marlowe.Observation
+    }
+  | EvalObservation
+    {
+      environment :: Marlowe.Environment
+    , state :: Marlowe.State
+    , observation :: Marlowe.Observation
+    }
+    deriving (Eq, Show)
+
+instance FromJSON Request where
+  parseJSON =
+    A.withObject "Request"
+      $ \o ->
+        (o A..: "request" :: A.Parser String)
+          >>= \case
+            "test-roundtrip-serialization" -> TestRoundtripSerialization <$> o A..: "typeId" <*> o A..: "json"
+            "generate-random-value"        -> GenerateRandomValue <$> o A..: "typeId" <*> o A..:? "size" <*> o A..:? "seed"
+            "compute-transaction"          -> ComputeTransaction <$> o A..: "transactionInput" <*> o A..: "coreContract" <*> o A..: "state"
+            "playtrace"                    -> PlayTrace <$> o A..: "transactionInputs" <*> o A..: "coreContract" <*> (POSIXTime <$> o A..: "initialTime")
+            "eval-value"                   -> EvalValue <$> o A..: "environment" <*> o A..: "state" <*> o A..: "value"
+            "eval-observation"             -> EvalObservation <$> o A..: "environment" <*> o A..: "state" <*> o A..: "observation"
+            request                        -> fail $ "Request not understood: " <> show request <> "."
+
+instance ToJSON Request where
+  toJSON TestRoundtripSerialization{..} =
+    A.object
+      [
+        "request" A..= ("test-roundtrip-serialization" :: String)
+      , "typeId" A..= typeSerialized
+      , "json"  A..= valueSerialized
+      ]
+  toJSON GenerateRandomValue{..} =
+    A.object
+      [
+        "request" A..= ("generate-random-value" :: String)
+      , "typeId" A..= typeSerialized
+      , "size" A..= size
+      , "seed" A..= seed
+      ]
+  toJSON ComputeTransaction{..} =
+    A.object
+      [
+        "request" A..= ("compute-transaction" :: String)
+      , "transactionInput" A..= transactionInput
+      , "coreContract" A..= contract
+      , "state" A..= state
+      ]
+  toJSON PlayTrace{..} =
+    A.object
+      [
+        "request" A..= ("playtrace" :: String)
+      , "transactionInputs" A..= transactionInputs
+      , "coreContract" A..= contract
+      , "initialTime" A..= getPOSIXTime initialTime
+      ]
+  toJSON EvalValue{..} =
+    A.object
+      [
+        "request" A..= ("eval-value" :: String)
+      , "environment" A..= environment
+      , "state" A..= state
+      , "value" A..= value
+      ]
+  toJSON EvalObservation{..} =
+    A.object
+      [
+        "request" A..= ("eval-value" :: String)
+      , "environment" A..= environment
+      , "state" A..= state
+      , "observation" A..= observation
+      ]
+
+data Response =
+    InvalidRequest
+    {
+      errorInvalid :: String
+    }
+  | UnknownRequest
+  | RequestResponse
+    {
+      valueResponse :: A.Value
+    }
+  | RequestNotImplemented
+  | RequestTimeOut
+  | ResponseFailure
+    {
+      failureResponse :: String
+    }
+    deriving (Eq, Ord, Read, Show)
+
+instance FromJSON Response where
+    parseJSON (A.String "UnknownRequest") = return UnknownRequest
+    parseJSON (A.String "RequestNotImplemented") = return RequestNotImplemented
+    parseJSON (A.Object v) = (InvalidRequest <$> v A..: "invalid-request") <|> (RequestResponse <$> v A..: "request-response")
+    parseJSON _ = fail "Response must be either a string or an A.object"
+
+instance ToJSON Response where
+  toJSON UnknownRequest = "UnknownRequest"
+  toJSON RequestNotImplemented = "RequestNotImplemented"
+  toJSON RequestTimeOut = "RequestTimeOut"
+  toJSON (InvalidRequest err) = A.object . pure $ "invalid-request" A..= err
+  toJSON (RequestResponse res) = A.object . pure $ "request-response" A..= res
+  toJSON (ResponseFailure err) = A.object . pure $ "invalid-request" A..= err
```
